Citing \cite{InfH} properly.

Kabellose Technologien sind in abgelegenen Gebieten wichtig \cite{APCW2006}.


When a new student is applying for the HTBLA Leonding he or she has to fill out the application form and bring to the school office.
The person in charge of the application process has to enter the data into an access database provided by the system administrator.
This process is time consuming and tedious especially because there are hundreds of applications every year.
The goal of this project is to create an application that simplifies the this process for the school office staff
and since those do usually not have a computer science background the application has to be easy to use and intuitive.

The app has to be able to handle multiple photos of the same application because it consists of multiple pages.
It also has to contain some validation feature to allow the user to validate the output of the document understanding model
because we are working with important data that must not be entered incorrectly.

Due to data protection laws the document understanding model has to be deployed on premise in the school network and not store
any data unneccessarily.

The validated data needs to be entered into the access database provided by the school's system administrator.
The database contains two important tables for the application.
A table for the applicant's data and a table for the legal guardian's data.
Both of those tables contain highly confidential data like a social security number, home address and religion, etc.

After the deadline for the applications the contents of the access database will be written to an excel file which will in turn be importet into \gls{sokrates}.
